Realistically Interesting Domains for Probabilistic Planners

### 2014-04-09 FinalPaper/paper.tex
Remove some old text
Add label for domain

This paper presents a new domain involving Unmanned Aerial Vehicles (UAVs) that have to cooperate to deliver data packages from one UAV to the base station. To match this problem with an appropriate planner, this paper presents an overview of other interesting domains and probabilistic planners that were involved in the redefinition of an interesting planning problem. By evaluating the domains with the help of the probabilistic interestingness baseline test introduced by Little et al. \cite{little2007probvsreplan} a recommendation will be made for a suitable planner to match the UAV problem.
%This paper presents an overview of interesting domains and concurrent planners that were involved in the redefinition of an interesting planning problem. An interesting currently relevant domain is proposed and evaluated amongst previously defined domains. By using the probabilistic interestingness baseline test as introduced by Little et al. \cite{little2007probvsreplan} a recommendation will be made for the optimal planner to match this problem.

@@

%Little and Thi\'ebaux have developed a baseline test in
%\cite{little2007probvsreplan} to evaluate the problems of the fifth International
%Planning Competition (IPC-5). This test determines if a planning problem is
%`probabilistically interesting'. Problems that fail this test are classical
%planning problems in disguise. Knowing this it is easy to design a problem
%where a replanner performs badly or incredibly well.
%While it is interesting to make problems harder and invent better planning
%algorithms to solve those probabilistic complex problems, we evaluate whether
%or not these problems are coherent with real-world situations.
%The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
%which can design domains that are more probabilistically interesting. The top
%performers were PROST \cite{keller2012prost} and \textsc{Glutton}
%\cite{kolobov2012glutton}.

%The main contribution of this paper is an evaluation of FF-Replan versus a
%probabilistically state of the art planner \textsc{Gourmand} in the realistically
%augmented domains of IPPC-11. If these domains fail the baseline test proposed
%by Little et al\., they would translate to classical planning problems in
%disguise and could be easily solved by FF-Replan.

%\begin{itemize}
%	\item Describe probabilistic planning problem
%	\item Introduce planning for uncertainty
%	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
%	\item Introduce the qualities of replanning and the second planning algorithm
%	\item Describe the need for a new domain for real world applications
%	\item Describe the goal and tools used to reach this goal
%\end{itemize}

@@

%% TODO maybe UAVs can be on or of too, so it's forced to use a further UAV.
%% TODO what's also interesting is that Amazon.com uses drones for package deliveries

@@

%Following existing domains were said to be probabilistically interesting:
%
%\begin{itemize}
%	\item Drive
%	\item Exploding blocksworld
%	\item Pitchcatch
%	\item Schedule
%	\item Tireworld
%\end{itemize}

\section{Domains}

@@

%Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et al.'s baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.

@@

%The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty. The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners. IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.

%\subsection{IPPC-04 Domains}
%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
%

@@

%However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
The \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR$^2$TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ by relying on the fact that a successful policy can be produced by solving a MDP-FH $M(h)$ for a smaller horizon $h < H$.
%LR$^2$TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.

@@

\subsection{\textsc{Glutton}}
The \textsc{Glutton} planner enhances LR$^2$TDP to cope with large branching factors by using several optimization techniques. It employs LR$^2$TDP in an off-line fashion by initializing the algorithm with the \emph{Max-Reward} heuristic that places an upper bound on the optimal value function $V^*$. It optimizes for large branching factors by performing the transition function in a subset of transition states $s'$. It distinguished between \emph{exogenous} effects caused by natural dynamics and \emph{pure} effects caused by the action itself and a mixed of both. It also utilized the saved memory space caused by mapping only the converged states in the hash-table by using the free space as cache for storing successor states computed using the transition function.
Since \textsc{Glutton} subsamples the transition function, it may not know a good action to perform in states it missed due to subsampling. To compensate for these states, \textsc{Glutton} has to resort to a \emph{default policy}. \todo{Wel of niet de default policy uitleggen}.
%---------------------------------------------------------------------
%During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT. This caused to wonder whether LRTDP planners could outperform UCT based systems.  UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states. Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity. At the IPPC-11 \textsc{Glutton} was an offline LRTDP based planner that came second. As PROST employed UCT in an online manner, \textsc{Gourmand} is an online adaptation of the \textsc{Glutton} algorithm to test whether LRTDP performs better if it is employed online.
%
%UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past. This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.

When however dealing with large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime. Such problems are far better solved using online planners that find an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state.
%This is done by choosing a certain lookahead value $L$ and solving the MDP $M_s(L)$ to solve $M_0(H)$ where L $<$ H and then select $\pi^*_L(s,L)$ using the evaluation criteria. This lookahead value is determined using the per-process time constraint.

@@

\subsubsection{PROST}

\subsubsection{FF-H+}

%\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
%
%Hindsight optimization is an online technique that evaluates one-step-reachable
%states by sampling future outcomes to generate multiple non-stationary planning
%problems which are deterministic and can be used using search. It re-interprets
%FF-Replan's~\cite{FFReplan} strategy randomly generating a set of non-stationary
%determinized problems and combining their solutions.

%\subsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
%Hindsight optimization has enjoyed some success for online probabilistic
%planning. Although it has proven to be effective for many domains, it is
%computationally expensive. This paper presents significant improvements.  1) a
%method for detecting potential useful actions, 2) exploit determinism in the
%domain by reusing relevant plans, 2) improves action evaluation by increasing
%the chance that at least one deterministic plan reaches a goal.

%\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
%% might not be necessary?
%Graphplan is a successful planning algorithm for classical STRIPS domains. This
%paper explores the extend it can be used in \emph{probabilistic} domains. The
%paper discusses two variations of Graphplan: PGraphplan and TGraphplan.
%PGraphplan produces an optimal plan, while TGraphplan produces a sub-optimal
%plan but it has increased speed. By comparing the speed and quality of the
%two planners the authors are able to estimate how far they are from the ideal.

%\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
% not necessary?

%\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
%
%For household robot planning, it appears easy, but actually involves
%uncertainty. For tidying things up objects might not be there, or sensing
%operations might tell things wrong. This paper looks into conditions for
%classical planning in a replanning loop in order to solve nondeterministic
%partially observable open domains This paper looks into conditions for
%classical planning in a replanning loop in order to solve nondeterministic
%partially observable open domains.

%\subsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
%
%In this paper a probabilistic plan graph heuristic is described which computes
%information about the interaction between actions and between propositions.
%This information is used to find better relaxed plans to compute the
%probability of success. This information guides a forward state space search
%for high probability, non-branching seed plans. These plans are then used in
%a planning and scheduling system that handles unexpected outcomes by runtime
%replanning.

%\subsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
% I don't think one is valuable

@@

%\section{Some papers}
%
%\begin{itemize}
%	\item \cite{Hoffmann01theff}
%	\item \cite{FFReplan}
%	\item \cite{teichteil2010incremental}
%	\item \cite{yoon2008probabilistic}
%	\item \cite{teichteil2012fast}
%	\item \cite{bonet2011planning}
%	\item \cite{taig2013translation}
%	\item \cite{martin2013progressive}
%	\item \cite{taig2013conformant}
%	\item \cite{2013workshop}
%	\item \cite{nebel2013much}
%	\item \cite{little2007probvsreplan}
%	\item \cite{keller2012prost}
%	\item \cite{kolobov2012glutton}
%	\item \cite{sanner2008rddl}
%	\item \cite{kolobov2012gourmand}
%\end{itemize}

>>>>

This paper presents a new domain involving Unmanned Aerial Vehicles (UAVs) cooperating to deliver data packages from one UAV to the base station. To match this problem with an appropriate planner, this paper presents an overview of other interesting domains and probabilistic planners that were involved in the redefinition of an interesting planning problem. By evaluating the domains with the help of the probabilistic interestingness baseline test introduced by Little et al. \cite{little2007probvsreplan} a recommendation will be made for a suitable planner to match the UAV problem.

@@

@@

\todo{TODO maybe UAVs can be on or of too, so it's forced to use a further UAV.}
\todo{TODO what's also interesting is that Amazon.com uses drones for package deliveries}

@@

%---------------------------------------------------------------------------------------------------------------------------------

\section{Domains}
\label{sec:domains}

@@

@@

%---------------------------------------------------------------------------------------------------------------------------------

@@

The \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR$^2$TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ by relying on the fact that a successful policy can be produced by solving a MDP-FH $M(h)$ for a smaller horizon $h < H$.

@@

\subsection{\textsc{Glutton}}
The \textsc{Glutton} planner enhances LR$^2$TDP to cope with large branching factors by using several optimization techniques. It employs LR$^2$TDP in an off-line fashion by initializing the algorithm with the \emph{Max-Reward} heuristic that places an upper bound on the optimal value function $V^*$. It optimizes for large branching factors by performing the transition function in a subset of transition states $s'$. It distinguished between \emph{exogenous} effects caused by natural dynamics and \emph{pure} effects caused by the action itself and a mixed of both. It also utilized the saved memory space caused by mapping only the converged states in the hash-table by using the free space as cache for storing successor states computed using the transition function.
Since \textsc{Glutton} subsamples the transition function, it may not know a good action to perform in states it missed due to subsampling. To compensate for these states, \textsc{Glutton} has to resort to a \emph{default policy}. \todo{Wel of niet de default policy uitleggen}.
%---------------------------------------------------------------------

When however dealing with large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime. Such problems are far better solved using online planners that find an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state.

@@

\subsubsection{PROST ?}

@@
